Regular singular Volterra equations on complex domains

### 2024-05-01 sima/reg-sing-volterra_sima.tex
Revise definition of Laplace transform

By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:sing-bound}
\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
\end{equation}
whenever $|\zeta| < \delta$. \textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:} \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} \textcolor{pink}{by rewriting the integral in the definition of $\chi$:}
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\color{orange}
For $\tau\in\C$
\begin{equation}
    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
\end{equation}
so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate". I'm not very confortable with rotations, so probably I'll not add this complication. I'm also afraid we should be more carefull with these mooving domains, if we allow rotations. So maybe better not make things too complicated for the sake of generality. We have a good list of examples that fit in our pictures. 
\color{black}
\end{proof}
\subsubsection{Regularity}\label{sec:asymptotics}
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}. The proofs of the Proposition below can be combined together.}
Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
\begin{proposition}\label{prop:asymptotic at zero}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
\end{proposition}

@@

for any integration path that stays within $\near$. \textcolor{blue}{Since $\domain$ is star-shaped around $\zeta = 0$, so is $\near$. \textcolor{orange}{[\ldots]}} \textcolor{red}{Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path} \textcolor{brown}{Since $\near$ \textcolor{magenta}{is star-shaped [why?]} at $\zeta=0$, the path of integration can be chosen to be a segment } $\zeta = t \zeta(a)$, with $t \in (0, 1]$.

@@

Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. Choose some $\lambda > \lambda_\Delta$. By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} there is some $M\in\R_{>0}$ for which

@@

Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then \textcolor{red}{we can make our bound} there is an uniform bound over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:

@@

\textcolor{red}{Now, we just want to} Next, we show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{red}{that leaves} originating from $\zeta=\alpha$ \textcolor{red}{at angle} in the direction of $\theta$. \color{red} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}%\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It is a function on the frequency domain because it depends on the frequency variable $z$.
\color{brown}
Let $\Pi_\Lambda^\theta:=\{z\in\C \,\vert \, \Re(z e^{i\theta})>\Lambda\}$. If $\Gamma_{\zeta, \alpha}^\theta$ is contained in $\domain_\alpha$, the Laplace transform 
\[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\domain_\alpha)\to\holo(\Pi_\Lambda^\theta)\]
is defined by
\begin{equation}\label{laplace:int} 
(\laplace_{\zeta, \alpha}^{\theta} \varphi)(z) := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
\color{black}
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the \textcolor{red}{expected} semigroup law \cite[Section~1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.

>>>>

By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
\begin{equation}\label{eqn:sing-bound}
\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
\end{equation}
whenever $|\zeta| < \delta$. \textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:} \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} \textcolor{pink}{by rewriting the integral in the definition of $\chi$:}
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta.
\end{align*}
Exponentiating both sides \textcolor{blue}{shows that}
\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$. Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$. It follows, as discussed above, that $\hardpart \solproto = \solproto$. 
\color{orange}
For $\tau\in\C$
\begin{equation}
    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
\end{equation}
so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate". I'm not very confortable with rotations, so probably I'll not add this complication. I'm also afraid we should be more carefull with these mooving domains, if we allow rotations. So maybe better not make things too complicated for the sake of generality. We have a good list of examples that fit in our pictures. 
\color{black}
\end{proof}
\subsubsection{Regularity}\label{sec:asymptotics}
%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}. The proofs of the Proposition below can be combined together.}
Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
\begin{proposition}\label{prop:asymptotic at zero}
Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
\end{proposition}

@@

for any integration path that stays within $\near$. \textcolor{blue}{Noting} that $\near$ is \textcolor{blue}{star-shaped by construction, we} use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:

@@

Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. Choose some $\lambda > \lambda_\Delta$. By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} \textcolor{blue}{there is some $M\in\R_{>0}$} for which

@@

Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:

@@

\textcolor{red}{Now, we just want to} \textcolor{brown}{Next, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.

@@

Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$. For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$. This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a,a'\in\domain_\alpha$. 
Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain_\alpha$.
\subsection{The Laplace transform}
\subsubsection{Definition}
Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$. Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} \textcolor{blue!50}{that leaves} $\zeta=\alpha$ \textcolor{blue!50}{at angle} $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
\[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
is defined for all $\sigma > -1$ and $\Lambda \in \R$. Its action on a function $\varphi$ is given by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
\color{red} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula
\begin{equation}%%\label{laplace:int} 
\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
It is a function on the frequency domain because it depends on the frequency variable $z$.
Let $\Pi_\Lambda^\theta:=\{z\in\C \,\vert \, \Re(z e^{i\theta})>\Lambda\}$. If $\Gamma_{\zeta, \alpha}^\theta$ is contained in $\domain_\alpha$, the Laplace transform 
\[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\domain_\alpha)\to\holo(\Pi_\Lambda^\theta)\]
is defined by
\begin{equation}%%\label{laplace:int} 
(\laplace_{\zeta, \alpha}^{\theta} \varphi)(z) := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
\end{equation}
\subsubsection{Action on integral operators}\label{sec:L-int-op}
For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
for each $a \in \domain_\alpha$. It obeys the \textcolor{red}{expected} semigroup law \cite[Section~1.3]{mladenov2014advanced}
\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.
